---
title: "covid"
author: "Maryam GHEBLEH"
date: "26 mai 2022"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(tmaptools)
library(dplyr)
library(leaflet)
library(sf)
library(plotly)
library(albersusa)
library(cartogram)
library(htmlwidgets)



knitr::opts_chunk$set(echo = TRUE)
```
##Load the data and distribute the vaccine according to the age


Based on the age, I distributed 1 million vaccines.

The priority of the vaccines is explained below:

First) The people who had upper 65 years old and didn't have the second dose,
second)The people who had upper 65 years old and didn't have the booster dose,
third)The people who had the age between 18 to 65 years old and didn't have the second dose,
fourth)The people who had the age between 18 to 65 years old and didn't have the booster dose.




```{r }

##Load data
covid<-read.csv("C:/Users/Mgheblehgoydaragh/Desktop/Test/county_level_vaccination_data_for_washington.csv",sep = ",",na.strings=c("","NaN","NA") )

##getting geographic data

##load shapefile of the washington
my_map<-st_read("C:/Users/Mgheblehgoydaragh/Desktop/Test/Washington_Counties_with_Natural_Shoreline___washsh_area/Washington_Counties_with_Natural_Shoreline___washsh_area.shp")



## the priority with age plus 65
##age plus 65
covid<-covid %>%
  mutate(Delta_65=People.65..with.at.least.1.Dose...Resident - Population...65.Years.of.Age.with.a.First.Booster.Dose,## diffrences between first dose and third dose
    Deltafully_65=People.65..with.at.least.1.Dose...Resident - People.65..Fully.Vaccinated...Resident,## diffrences between first dose and second dose
    boost_65= People.65..Fully.Vaccinated...Resident-Population...65.Years.of.Age.with.a.First.Booster.Dose)## diffrences between second dose and third dose




##age 18-65
covid<-covid %>%
  mutate(Delta_18=People.18..with.at.least.1.Dose...Resident - Population...18.Years.of.Age.with.a.First.Booster.Dose,## diffrences between first dose and third dose
    Deltafully_18=People.18..with.at.least.1.Dose...Resident - People.18..Fully.Vaccinated...Resident,## diffrences between first dose and second dose
    boost_18= People.65..Fully.Vaccinated...Resident-Population...18.Years.of.Age.with.a.First.Booster.Dose,##diffrences between second dose and third dose
    ratio_18= round(202314*boost_18/sum(boost_18)))## The remaining vaccines for third dose are low (202314), then I distributed the remaining vaccines based on the number of the people who didn't do booster vaccine in all counties



```

## Showing the results on the maps



```{r }


##join: combining data with the map

map_covid<-my_map %>% left_join(covid,by=c("COUNTY"="COUNTY"))


##data on the map


## Second dose

p1<-plot_ly(map_covid) %>% 
  add_sf(
    geojson=~COUNTY,
    color = ~COUNTY, 
    split = ~ COUNTY, 
    span = I(1),
    text = ~paste('County: ', COUNTY,
                   '<br>',
      'Second dose_plus65: ', Deltafully_65,#distribution of vaccines for people who had not second dose (upper 65 years old)
      '<br>',
      'Booster_plus65: ', boost_65,#distribution of vaccines for people who had not booster dose(upper 65 years old)
      '<br>',
      'Second dose_18to65: ', Deltafully_18,#distribution of vaccines for people who had not second dose(between 18 and 65 years old)
      '<br>',
      'Booster_18to65: ', ratio_18),#distribution of vaccines for people who had not booster dose(between 18 and 65 years old)
    type='scatter',
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = TRUE) 

##export HTML

#saveWidget(ggplotly(p1), file = "Covid_map.html")





```




